Generate data for multispecies modeling, including diet!

### 2020-09-11 NOBAmsdiets.Rmd
by layer plots, still breaking on by polygon

```{r detdiet-vis}

# look at a single species/age combo from above

# how many polygons included? how many layers per polygon have data?

# are there differences by layer within a polygon?

# are there differences by polygon? (aggregate layers)

>>>>

```{r detdiet-vis1}

# look at a single species/age combo from above
#    agecl 5 (age 9-10) cod
cod5det <- ms_detaileddiet %>%
  filter(species=="North_atl_cod",
         agecl==5)

# how many polygons included? how many layers per polygon have data?
cod5det %>% group_by(time.days, polygon, layer) %>% tally()

# are there differences by layer within a polygon?
#    polygons 12 and 19 are on the slope, have most layers with agecl 5 cod
cod5det1219 <- cod5det %>%
  filter(polygon %in% c(12,19))

plist2 = lapply(split(cod5det1219, cod5det1219$polygon), function(d) {
  ggplot(d, aes(time.days/365, atoutput, fill=prey)) + 
    geom_bar(stat = "identity") +
    facet_wrap(polygon~layer) +
    xlab("year") +
    ylab("diet tons") +
    theme_tufte() +
    theme(legend.position="bottom")
})
```

### Diets by polygon and layer {.tabset}

#### Cod agecl 5 polygon 12
```{r, fig.width=9, fig.height=9}
plist2$'12'
```

#### Cod agecl 5 polygon 19
```{r, fig.width=9, fig.height=9}
plist2$'19'
```

```{r detdiet-vis2}
# are there differences by polygon? (aggregate layers)
cod5det_agg <- cod5det %>%
  group_by(species, agecl, time.days, polygon, prey) %>%
  summarise(polytons = sum(atoutput))

ggplot(cod5det_agg, aes(time.days/365, polytons, fill=prey)) + 
    geom_bar(stat = "identity") +
    facet_wrap(polygon) +
    xlab("year") +
    ylab("diet tons") +
    theme_tufte() +
    theme(legend.position="bottom")
